---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# statpsych: Statistical Methods for Psychologists
[![CRAN status](https://www.r-pkg.org/badges/version/statpsych)](https://CRAN.R-project.org/package=statpsych)
![Download count](https://cranlogs.r-pkg.org/badges/last-month/statpsych)


[statpsych](https://github.com/dgbonett/statpsych) implements confidence interval and sample size methods that are especially useful in psychological research. The methods can be applied in 1-group, 2-group, paired-samples, and multiple-group designs and to a variety of parameters including means, medians, proportions, slopes, standardized mean differences, standardized linear contrasts of means, plus several measures of correlation and association. The confidence intervals and sample size functions are applicable to single parameters as well as differences, ratios, and linear contrasts of parameters.  The sample size functions can be used to approximate the sample size needed to estimate a parameter or function of parameters with desired confidence interval precision or to perform a variety of hypothesis tests (directional two-sided, equivalence, superiority, noninferiority) with desired power. For details, see: <https://csass.ucsc.edu/self-study%20courses/statistical_methods.html>.

## Installation

You can install the currently-released version from CRAN with this R
command:

```{r install, eval=FALSE}
install.packages("stapsych")
```

Alternatively, you can install the latest development version from GitHub with these R
commands:

```{r install_github, eval=FALSE}
install.packages("devtools")
devtools::install_github("dgbonett/statpsych")
```


## Feedback, issues, and contributions
Submit feedback, suggestions, and bugs to github [here](https://github.com/dgbonett/statpsych/issues/new).  

